---
title: "Assignment-3"
author: "Dushyant Goel"
date: "2024-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r cars}
library(tidyverse)
library(Stat2Data)
data("Hawks")
```

# 1. Visualization

## Q1

```{r}
hawksSmall <-
  drop_na(select(
                 Hawks,
                 Age,
                 Day,
                 Month,
                 Year,
                 CaptureTime,
                 Species,
                 Wing,
                 Weight,
                 Tail))
```

```{r}
dim(hawksSmall)
```

```{r}
head(hawksSmall, 5)
```
## Q2

```{r}
ggplot(hawksSmall, aes(x = Weight)) + geom_histogram(binwidth = 10.0)
```

## Q3

```{r}
ggplot(hawksSmall, aes(x = Tail)) + geom_density(adjust = 0.5) + ylab("Count")
ggplot(hawksSmall, aes(x = Tail)) + geom_density(adjust = 2) + ylab("Count")
```

The plots differ by `bandwidth`, which is a measure of smoothening applied to the underlying histogram data.\
The plot #1 is less smooth than plot #2, capturing finer details (or noise).\
Hence, we expect more modes in plot #1\

Plot | Number of modes \
adjust=0.5 | 4 \
adjust=2 | 2 \

## Q4
```{r}
ggplot(
       hawksSmall,
       aes(x = Tail, color = Species)) +
  geom_density(adjust = 2) + ylab("Count")
```

## Q5

```{r}
ggplot(
       hawksSmall,
       aes(x = Tail, y = Species, fill = Species)) +
  geom_violin() + xlab("Tail (mm)") + ylab("Density")
```

## Q6

```{r}
ggplot(hawksSmall, aes(y = Weight, x = Tail, colour = Species)) +
  xlab("Tail (mm)") +
  ylab("Weight (g)") +
  geom_point()
```

1. Aesthetics present are `Weight (g)` along y, `Tail (mm)` along x, `Species` along colour, `Species` along shape.
2. `geom_point` is the Glyph.
3. The overlapping colour and shape of the glyph are the visual cues for the species.

## Q7
```{r}
ggplot(hawksSmall, aes(x = Tail, y = Weight, colour = Species)) +
  xlab("Tail (mm)") +
  ylab("Weight (mm)") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~Species)
```

1. The visual cues being used are shape, colour and the direction of the trend line.
2. The tail length and weight are positively co-related


## Q8
```{r}
largest_row <- hawksSmall %>%
  filter(Weight == max(Weight)) %>%
  select(Weight, Tail)
```

```{r}
ggplot(hawksSmall, aes(y = Weight, x = Tail, colour = Species)) +
  xlab("Tail (mm)") + ylab("Weight (g)") +
  geom_point() +
  geom_curve(
             x = 196,
             xend = 196,
             y = 1800,
             yend = 2030,
             arrow = arrow(length = unit(0.3, "cm")),
             curvature = 0.1,
             colour = "black") +
  geom_text(x = 200,
            y = 1750,
            label = "heaviest hawk",
            colour = "black",
            size = 3)
```



