---
title: "Assignment-3"
author: "Dushyant Goel"
date: "2024-10-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r cars}
library(tidyverse)
library(Stat2Data)
data("Hawks")
```

# 1. Visualization

## Q1

```{r}
hawksSmall <-
drop_na(select(Hawks, Age, Day, Month, Year, CaptureTime, Species ,Wing, Weight, Tail))
```

## Q2

```{r}
ggplot(hawksSmall, aes(x=Weight)) + geom_histogram(binwidth = 10.0)
```

## Q3

```{r}
ggplot(hawksSmall, aes(x=Tail)) + geom_density(adjust=0.5) +ylab("Count")
ggplot(hawksSmall, aes(x=Tail)) + geom_density(adjust=2) +ylab("Count")
```

The plots differ by `bandwidth`, which is a measure of smoothening applied to the underlying histogram data.\
The plot #1 is less smooth than plot #2, capturing finer details (or noise).\
Hence, we expect more modes in plot #1\

Plot | Number of modes \
adjust=0.5 | 4 \
adjust=2 | 2 \

## Q4
```{r}
ggplot(hawksSmall, aes(x=Tail, color=Species)) + geom_density(adjust=2) +ylab("Count")
```

## Q5

```{r}
ggplot(hawksSmall, aes(x=Tail, y=Species, fill=Species)) + geom_violin() + xlab("Tail (mm)") +ylab("Density")
```
## Q6

```{r}
ggplot(hawksSmall, aes(y=Weight, x=Tail, colour=Species)) + xlab("Tail (mm)") + ylab("Weight (g)") +geom_point()
```

1. Aesthetics present are `Weight (g)` along y, `Tail (mm)` along x, `Species` along colour, `Species` along shape.
2. `geom_point` is the Glyph.
3. The overlapping colour and shape of the glyph are the visual cues for the species.

## Q7
```{r}

```
# Finite probability spaces
