---
title: "Assignment-3"
author: "Dushyant Goel"
date: "2024-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r cars}
library(tidyverse)
library(Stat2Data)
data("Hawks")
```

# 1. Visualization

## Q1

```{r}
hawksSmall <-
  drop_na(select(
                 Hawks,
                 Age,
                 Day,
                 Month,
                 Year,
                 CaptureTime,
                 Species,
                 Wing,
                 Weight,
                 Tail))
```

```{r}
dim(hawksSmall)
```

```{r}
head(hawksSmall, 5)
```
## Q2

```{r}
ggplot(hawksSmall, aes(x = Weight)) + geom_histogram(binwidth = 10.0)
```

## Q3

```{r}
ggplot(hawksSmall, aes(x = Tail)) + geom_density(adjust = 0.5) + ylab("Count")
ggplot(hawksSmall, aes(x = Tail)) + geom_density(adjust = 2) + ylab("Count")
```

The plots differ by `bandwidth`, which is a measure of smoothening applied to the underlying histogram data.\
The plot #1 is less smooth than plot #2, capturing finer details (or noise).\
Hence, we expect more modes in plot #1\

Plot | Number of modes \
adjust=0.5 | 4 \
adjust=2 | 2 \

## Q4
```{r}
ggplot(
       hawksSmall,
       aes(x = Tail, color = Species)) +
  geom_density(adjust = 2) + ylab("Count")
```

## Q5

```{r}
ggplot(
       hawksSmall,
       aes(x = Tail, y = Species, fill = Species)) +
  geom_violin() + xlab("Tail (mm)") + ylab("Density")
```

## Q6

```{r}
ggplot(hawksSmall, aes(y = Weight, x = Tail, colour = Species)) +
  xlab("Tail (mm)") +
  ylab("Weight (g)") +
  geom_point()
```

1. Aesthetics present are `Weight (g)` along y, `Tail (mm)` along x, `Species` along colour, `Species` along shape.
2. `geom_point` is the Glyph.
3. The overlapping colour and shape of the glyph are the visual cues for the species.

## Q7
```{r}
ggplot(hawksSmall, aes(x = Tail, y = Weight, colour = Species)) +
  xlab("Tail (mm)") +
  ylab("Weight (mm)") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~Species)
```

1. The visual cues being used are shape, colour and the direction of the trend line.
2. The tail length and weight are positively co-related


## Q8
```{r}
largest_row <- hawksSmall %>%
  filter(Weight == max(Weight)) %>%
  select(Weight, Tail)
```

```{r
ggplot(hawksSmall, aes(y = Weight, x = Tail, colour = Species)) +
  xlab("Tail (mm)") + ylab("Weight (g)") +
  geom_point() +
  geom_curve(
             x = 196,
             xend = 196,
             y = 1800,
             yend = 2030,
             arrow = arrow(length = unit(0.3, "cm")),
             curvature = 0.1,
             colour = "black") +
  geom_text(x = 200,
            y = 1750,
            label = "heaviest hawk",
            colour = "black",
            size = 3)
```


# 2. Finite probability spaces
## 2.1 Sampling with replacement
### Q1

$$
P(A) = \binom{22}{z} \left(\frac{7}{10}\right)^{22} \left(\frac{3}{10}\right)^{22-z}
$$

### Q2

```{r}
prob_red_spheres <- function(z) {
  total_spheres <- 10
  red_spheres <- 3
  blue_spheres <- 7
  trials <- 22

  return(choose(trials, z) *
           (red_spheres / total_spheres)^z *
           (blue_spheres / total_spheres)^(trials - z))
}

prob_red_spheres(10)
```

```{r}
num_reds <- seq(22)
prob <- prob_red_spheres(num_reds)
prob_by_num_reds <- data.frame(num_reds, prob)

head(prob_by_num_reds, 3)
```

### Q4

```{r}
ggplot(prob_by_num_reds, aes(x = num_reds, y = prob)) +
  xlab("Number of reds") +
  ylab("Probability") +
  geom_line()
```

### Q5

```{r}
itermap <- function(.x, .f) {
  result <- list()
  for(item in .x) {
    result <- c(result, list(.f(item)))
  }
  return(result)
}

itermap(c(1, 2, 3), function(x) {
  return(c(x, x^2))
})

itermap_dbl <- function(.x, .f) {
  result <- numeric(length(.x))
  for(i in 1:length(.x)) {
    result[i] <- .f(.x[[i]])
  }
  return(result)
}

itermap_dbl(c(1, 2, 3), function(x){ 
  return(x^3)
})

```
```{r}
num_trials <- 1000
set.seed(0)

sampling_with_replacement_simulation <- data.frame(trial = 1:num_trials) %>%
  mutate(sample_balls = itermap(.x = trial,
    function(x) {
      sample(10,
        22,
        replace = TRUE
      )
    }
  )) %>%
  mutate(num_reds = itermap_dbl(.x = sample_balls, function(.x) {
    sum(.x <= 3)
  }))

```

### Q6

```{r}
num_reds_in_simulation <- sampling_with_replacement_simulation %>%
  pull(num_reds)

prob_by_num_reds <- prob_by_num_reds %>%
  mutate(predicted_prob = itermap_dbl(.x = num_reds,
      function(.x) sum(num_reds_in_simulation == .x)
    ) / num_trials
  )
```

### Q7
```{r}
prob_by_num_reds %>%
  rename(TheoreticalProbability = prob,
         EstimatedProbability = predicted_prob) %>%
  ggplot() +
  geom_line(aes(x = num_reds, y = TheoreticalProbability)) +
  geom_line(aes(x = num_reds, y = EstimatedProbability)) +
  theme_bw() +
  xlab("Number of reds") +
  ylab("Probabilities")
```

## 2.2 Sampling without replacement

### Q1
```{r}
# Step 1
set.seed(1)
# Step 2
num_trials <- 1000
sample_size <- 10
# Step 3
sampling_without_replacement_simulation <- data.frame(trials = 1:num_trials) %>%
  mutate(sample_balls = itermap(.x = trials, function(x) {
    sample(100, 10, replace = FALSE)
  }))
# Step 4
sampling_without_replacement_simulation <-
  sampling_without_replacement_simulation %>%
  mutate(num_red = itermap_dbl(.x = sample_balls, function(.x) {
    sum(.x <= 50)
  }), num_blue = itermap_dbl(.x = sample_balls, function(.x) {
    sum(.x > 50 & .x <= 80)
  }), num_green = itermap_dbl(.x = sample_balls, function(.x) {
    sum(.x > 80)
  }))
# Step 5
sampling_without_replacement_simulation <-
  sampling_without_replacement_simulation %>%
  mutate(min_count = pmin(num_red, num_blue, num_green))
# Step 6
zero_prop <-
  sum(sampling_without_replacement_simulation$min_count == 0) /
  num_trials

# sampling_without_replacement_simulation
zero_prop
```
